\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2018-09-26 bare_conf.tex
minor text updates

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{~\\[-0.4ex]\large Michael Shell\\[0.3ex]\normalsize}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: {\tt ...}}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large Homer Simpson\\[0.3ex]\normalsize}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: {\tt homer@thesimpsons.com}}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large James Kirk\\ and Montgomery Scott\\[0.3ex]\normalsize}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678-2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

@@

\begin{IEEEkeywords}
Anything; Something; Everything else.%
\end{IEEEkeywords}

@@

More than $250$ million poople worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}. During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world. However, computer vision is rapidly evolving field, and systems based on the aforementioned approaches often lack accuracy and reliability in real-world conditions. In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans. Many of the previuosly proposed electronic aids for the blind count on highly specialised hardware, for instance smart glassess \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photosensors and cameras \cite{Larisa}. Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of the white cane. This project puts major emphasis on developing a tool, which seamlesly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone). This paper describes the high level architecture of the proposed technology aid for visually impaired people.

@@

Following the principles of participatory design \cite{Kensing}, \cite{Carroll} we included the final users into the design process of the system. Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution. During the six discussion sessions major attention was paid to:
\begin{enumerate}
\item Functionality and key features of the solution addressing real-life scenarios of visually impaired persons;
\item Technical feasibility, connecting user needs to the latest development in computer vision and assisted technologies;
\item Interface between the visually impaired person and the assisted technology;
\item Appearance, usability and potential costs of the final product. 
\end{enumerate}
Design process involved testing of the existing technological solutions (mobile phone apps) for assisting visually impaired persons {\color{red}(which ones have we tested?)}. Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from a project group. Strengths and weaknesses of the existing solutions are reflected in the design of the proposed system.

@@

%padalijimas i 2 komponentus man nelabai aiskus. As dalinciau i input (kameros, sensoriai), output (ausines, vibratoriu matricos), processing (local, remote). 
% tai kas dabar yra prie Inference, siulau perprazuot kaip Functionality, ka as minejau Method. Taip pat visa Results skyreli reiktu labiau susiet su Method. Reiktu, kad visi 4 Method pamineti punktai isrysketu ir Results. 
%Results skyrelyje nereiktu taip stipriai fokusuotis i kitu grupiu tyrimus ir juos cituoti. Rezultatai juk musu.
\textbf{Device} subsystem is a computational device the user currently uses for completing other daily tasks. It consists of sensors and actuators, integrated into smartphone-based computation core, which was chosen due its avialability to wide population, and capability to perform the required computations or forward visual information to the external server via Internet connection. Sensors are mounted on forehead belt include: RGB camera, depth camera, IMU. Actuator set consists of bone conductive headphones, and head belt for presenting tactile-feedback to the user. %We suggest to use bone conductive headphones, ...

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{~\\[-0.4ex]\large Michael Shell\\[0.3ex]\normalsize}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: {\tt ...}}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large Homer Simpson\\[0.3ex]\normalsize}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: {\tt homer@thesimpsons.com}}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large Andrius Budrionis\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University\\
Vilnius, Lithuania\\
Norwegian Centre for E-health Research\\
University Hospital of North Norway\\
Tromsø, Norway}}

@@

\begin{IEEEkeywords}
Computer vision; Mobile application; Travel aid; Tactile. %
\end{IEEEkeywords}

@@

More than $250$ million poople worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}. During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world. However, computer vision is rapidly evolving field, and systems based on the aforementioned approaches often lack accuracy and reliability in real-world conditions. In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans. Many of the previuosly proposed electronic aids for the blind count on highly specialised hardware, for instance smart glassess \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photosensors and cameras \cite{Larisa}. Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane. This project puts major emphasis on developing a tool, which seamlesly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone). This paper describes a high level architecture of the proposed technology aid for visually impaired people.

@@

Following the principles of participatory design \cite{Kensing}, \cite{Carroll} we included the final users into the design process of the system. Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution. During the six discussion sessions major attention was paid to:
\begin{enumerate}
\item Functionality and key features of the solution addressing real-life scenarios of visually impaired persons;
\item Technical feasibility, connecting user needs to the latest development in computer vision and assisted technologies;
\item Interface between the visually impaired person and the assisted technology;
\item Appearance, usability and potential costs of the final product. 
\end{enumerate}
Design process involved testing of the existing tmobile phone app (Seeing AI) for assisting visually impaired persons. Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from a project group. Strengths and weaknesses of the existing solutions are reflected in the design of the proposed system.

@@

%padalijimas i 2 komponentus man nelabai aiskus. As dalinciau i input (kameros, sensoriai), output (ausines, vibratoriu matricos), processing (local, remote). 
% tai kas dabar yra prie Inference, siulau perfrazuot kaip Functionality, ka as minejau Method. Taip pat visa Results skyreli reiktu labiau susiet su Method. Reiktu, kad visi 4 Method pamineti punktai isrysketu ir Results. 
%Results skyrelyje nereiktu taip stipriai fokusuotis i kitu grupiu tyrimus ir juos cituoti. Rezultatai juk musu.
\textbf{Device} subsystem is a computational device the user currently uses for completing other daily tasks. It consists of sensors and actuators, integrated into smartphone-based computational core, which was chosen due its avialability to wide population, and capability to perform the required computations or forward visual information to the external server via the Internet connection. Sensors are mounted on forehead belt include: RGB camera, depth camera, IMU. Actuator set consists of bone conductive headphones, and head belt for presenting tactile-feedback to the user. %We suggest to use bone conductive headphones, ...
